\section{2 Samuel 23 Comments}

\subsection{Numeric Nuggets}
\textbf{13: } Verse 37 has 13 words. Verse 29 has 13 unique words. The word ``a'' is found 13 times in the chapter.

\subsection{The List of Mighty Men}
Note that this is an inexact list.

There seem to have been a certain three mighty men who were the greatest of all of them. These are listed as Jashobeam the Tachmonite, Eleazar the son of Dodo, and Shammah the son of Agee the Hararite in II Samuel 23:8-12. These we might call the “top three.” Then, there was a second three. The first two of these are Abishai the son of Zeruiah and Benaiah the son of Jehoiada in II Samuel 23:18-23. The third of this second three was probably Joab, though he is not listed due to his final disloyalty to David when he followed Adonijah.

After these two sets of three there was a group called the ``thirty mighty men.'' These were not as great as the first two sets of three, but they were great enough to be considered ``mighty men'' over just regular officers in the army. Their number, even in II Samuel 23, does not seem to have been exactly thirty, as thirty-one names are listed, even once one subtracts the first two ``threes.'' Yet this name was probably a name they came to be known by, and once it caught on, it remained, even when their numbers swelled to larger than thirty. This is true in college football, for example, wherein the ``Big 10'' has twelve teams, the ``Big 12” has ten teams, and the ``Pac 10'' has twelve teams. Or something like that. Who can keep track? Anyway, the name ``thirty mighty men'' stuck, even when they had more members. In I Chronicles 11, the number had expanded by at least sixteen more members, though they are not actually called the ``thirty'' in this case. \\

\begin{compactenum}[1.]
	\item Jashobeam, the Tachmonite that sat in the seat, chief among the captains  (2 Samuel 23:8, 1 Chronicles 11:11)
	\item Eleazar the son of Dodo the Ahohite, one of the three mighty men with David (2 Samuel 23:9)
	\item Shammah the son of Agee the Hararite  (2 Samuel 23:11)
	\item Abishai, the brother of Joab, the son of Zeruiah  (2 Samuel 23:18)
	\item And Benaiah the son of Jehoiada, the son of a valiant man, of Kabzeel  (2 Samuel 23:20)
	\item Asahel the brother of Joab was one of the thirty (2 Samuel 23:24)
	\item Elhanan the son of Dodo of Beth-lehem (2 Samuel 23:24)
	\item Shammah the Harodite (2 Samuel 23:25)
	\item Elika the Harodite (2 Samuel 23:25)
	\item Helez the Paltite (2 Samuel 23:26)
	\item Ira the son of Ikkesh the Tekoite (2 Samuel 23:26)
	\item Abiezer the Anethothite (2 Samuel 23:27)
	\item Mebunnai the Hushathite (2 Samuel 23:27)
	\item Zalmon the Ahohite (2 Samuel 23:28)
	\item Maharai the Netophathite (2 Samuel 23:28)
	\item Heleb the son of Baanah, a Netophathite (2 Samuel 23:29)
	\item Ittai the son of Ribai out of Gibeah of the children of Benjamin (2 Samuel 23:29)
	\item Benaiah the Pirathonite (2 Samuel 23:30)
	\item Hiddai of the brooks of Gaash  (2 Samuel 23:30)
	\item Abi-albon the Arbathite (2 Samuel 23:31)
	\item Azmaveth the Barhumite (2 Samuel 23:31)
	\item Eliahba the Shaalbonite (2 Samuel 23:32)
	\item of the sons of Jashen, Jonathan (2 Samuel 23:32)
	\item Shammah the Hararite (2 Samuel 23:33)
	\item Ahiam the son of Sharar the Hararite (2 Samuel 23:33)
	\item Shammah the Hararite (2 Samuel 23:34)
	\item Ahiam the son of Sharar the Hararite (2 Samuel 23:34)
	\item Eliphelet the son of Ahasbai, the son of the Maachathite (2 Samuel 23:34)
	\item Eliam the son of Ahithophel the Gilonite (2 Samuel 23:34)
	\item Hezrai the Carmelite (2 Samuel 23:35)
	\item Paarai the Arbite (2 Samuel 23:35)
	\item Igal, the son on Nathan of Zobah  (2 Samuel 23:36)
	\item Bani the Gadite  (2 Samuel 23:36)
	\item Zelek, the Ammonite (2 Samuel 23:37)
	\item Naharai, the Beerothite (2 Samuel 23:37)
	\item Ira an Ithrite (2 Samuel 23:38)
	\item Gareb an Ithrite (2 Samuel 23:38)
	\item Uriah, the Hittiite (2 Samuel 23:39)
\end{compactenum}

