\chapter{2 Samuel 23 Notes \& Analysis}
\footnote{\textcolor[rgb]{0.00,0.25,0.00}{\hyperlink{2SamuelTOC}{Return to end of Table of Contents.}}}
\textcolor[rgb]{0.00,0.00,1.00}{Now these \emph{be} the last words of David. David the son of Jesse said, and the man \emph{who was} raised up on high, the anointed of the God of Jacob, and the sweet psalmist of Israel, said,}
[2]\textcolor[rgb]{0.00,0.00,1.00}{The Spirit of the LORD spake by me, and his word \emph{was} in my tongue.}
[3] \textcolor[rgb]{0.00,0.00,1.00}{The God of Israel said, the Rock of Israel spake to me, He that ruleth over men \emph{must be} just, ruling in the fear of God.}
[4] \textcolor[rgb]{0.00,0.00,1.00}{And \emph{he shall be} as the light of the morning, \emph{when} the sun riseth, \emph{even} a morning without clouds; \emph{as} the tender grass \emph{springing} out of the earth by clear shining after rain.}
[5] \textcolor[rgb]{0.00,0.00,1.00}{Although my house \emph{be} not so with God; yet he hath made with me an everlasting covenant, ordered in all \emph{things}, and sure: for \emph{this is} all my salvation, and all \emph{my} desire, although he make \emph{it} not to grow.}\\
\\
\P \textcolor[rgb]{0.00,0.00,1.00}{But \emph{the sons} of Belial \emph{shall be} all of them as thorns thrust away, because they cannot be taken with hands:}
[7] \textcolor[rgb]{0.00,0.00,1.00}{But the man \emph{that} shall touch them must be fenced with iron and the staff of a spear; and they shall be utterly burned with fire in the \emph{same} place.}
\section{2 Samuel 23:8}
\P \textcolor[rgb]{0.00,0.00,1.00}{These \emph{be} the names of the mighty men whom David had: The Tachmonite that sat in the seat, chief among the captains; the same \emph{was} Adino the Eznite: \emph{he lift up his spear} against eight hundred, whom he slew at one time.}\\
\\
David's mighty men:

\begin{enumerate}
\item Adino the Eznite,
\item Eleazar the son of Dodo the Ahohite,
\item Shammah the son of Agee the Hararite,
\item And Abishai, the brother of Joab, the son of Zeruiah (2 Samuel 23:18),
\item Benaiah the son of Jehoiada, the son of a valiant man, of Kabzeel (2 Samuel 23:20),
\item Asahel the brother of Joab \emph{was} one of the thirty (2 Samuel 23:24),
\item Elhanan the son of Dodo of Beth-lehem (2 Samuel 23:24),
\item Shammah the Harodite (2 Samuel 23:25),
\item Elika the Harodite (2 Samuel 23:25),
\item Helez the Paltite (2 Samuel 23:26),
\item Ira the son of Ikkesh the Tekoite (2 Samuel 23:26),
\item Helez the Paltite (2 Samuel 23:26),
\item Ira the son of Ikkesh the Tekoite (2 Samuel 23:26),
\item Abiezer the Anethothite (2 Samuel 23:27),
\item Mebunnai the Hushathite (2 Samuel 23:27),
\item Zalmon the Ahohite (2 Samuel 23:28),
\item Maharai the Netophathite (2 Samuel 23:28),
\item Heleb the son of Baanah, a Netophathite (2 Samuel 23:29),
\item Ittai the son of Ribai out of Gibeah of the children of Benjamin (2 Samuel 23:29),
\item Benaiah the Pirathonite (2 Samuel 23:30), 
\item Hiddai of the brooks of Gaash (2 Samuel 23:30),
\item Abi-albon the Arbathite (2 Samuel 23:31), 
\item Azmaveth the Barhumite (2 Samuel 23:31),
\item Eliahba the Shaalbonite (2 Samuel 23:32), 
\item of the sons of Jashen, Jonathan (2 Samuel 23:32),
\item Shammah the Hararite (2 Samuel 23:33), 
\item Ahiam the son of Sharar the Hararite (2 Samuel 23:33),
\item Eliphelet the son of Ahasbai, the son of the Maachathite (2 Samuel 23:34), 
\item Eliam the son of Ahithophel the Gilonite  (2 Samuel 23:34),
\item Hezrai the Carmelite (2 Samuel 23:35), 
\item Paarai the Arbite (2 Samuel 23:35),
\item Igal the son of Nathan of Zobah (2 Samuel 23:36), 
\item Bani the Gadite (2 Samuel 23:36),
\item Zelek the Ammonite (2 Samuel 23:37), 
\item Naharai the Beerothite, armourbearer to Joab the son of Zeruiah (2 Samuel 23:37), 
\item Ira an Ithrite (2Samuel 23:38), 
\item Gareb an Ithrite (2Samuel 23:38),
\item Uriah the Hittite (2Samuel 23:39)
\end{enumerate}


[9] \textcolor[rgb]{0.00,0.00,1.00}{And after him \emph{was} Eleazar the son of Dodo the Ahohite, \emph{one} of the three mighty men with David, when they defied the Philistines \emph{that} were there gathered together to battle, and the men of Israel were gone away:}
[10] \textcolor[rgb]{0.00,0.00,1.00}{He arose, and smote the Philistines until his hand was weary, and his hand clave unto the sword: and the LORD wrought a great victory that day; and the people returned after him only to spoil.}
[11] \textcolor[rgb]{0.00,0.00,1.00}{And after him \emph{was} Shammah the son of Agee the Hararite. And the Philistines were gathered together into a troop, where was a piece of ground full of lentiles: and the people fled from the Philistines.}
[12] \textcolor[rgb]{0.00,0.00,1.00}{But he stood in the midst of the ground, and defended it, and slew the Philistines: and the LORD wrought a great victory.}
[13] \textcolor[rgb]{0.00,0.00,1.00}{And three of the thirty chief went down, and came to David in the harvest time unto the cave of Adullam: and the troop of the Philistines pitched in the valley of Rephaim.}
[14] \textcolor[rgb]{0.00,0.00,1.00}{And David \emph{was} then in an hold, and the garrison of the Philistines \emph{was} then \emph{in} Beth-lehem.}
[15] \textcolor[rgb]{0.00,0.00,1.00}{And David longed, and said, Oh that one would give me drink of the water of the well of Beth-lehem, which \emph{is} by the gate!}
[16] \textcolor[rgb]{0.00,0.00,1.00}{And the three mighty men brake through the host of the Philistines, and drew water out of the well of Beth-lehem, that \emph{was} by the gate, and took \emph{it}, and brought \emph{it} to David: nevertheless he would not drink thereof, but poured it out unto the LORD.}
[17] \textcolor[rgb]{0.00,0.00,1.00}{And he said, Be it far from me, O LORD, that I should do this: \emph{is not this} the blood of the men that went in jeopardy of their lives? therefore he would not drink it. These things did these three mighty men.}
[18] \textcolor[rgb]{0.00,0.00,1.00}{And Abishai, the brother of Joab, the son of Zeruiah, was chief among three. And he lifted up his spear against three hundred, \emph{and} slew \emph{them}, and had the name among three.}
[19] \textcolor[rgb]{0.00,0.00,1.00}{Was he not most honourable of three? therefore he was their captain: howbeit he attained not unto the \emph{first} three.}
[20] \textcolor[rgb]{0.00,0.00,1.00}{And Benaiah the son of Jehoiada, the son of a valiant man, of Kabzeel, who had done many acts, he slew two lionlike men of Moab: he went down also and slew a lion in the midst of a pit in time of snow:}
[21] \textcolor[rgb]{0.00,0.00,1.00}{And he slew an Egyptian, a goodly man: and the Egyptian had a spear in his hand; but he went down to him with a staff, and plucked the spear out of the Egyptian's hand, and slew him with his own spear.}
[22] \textcolor[rgb]{0.00,0.00,1.00}{These \emph{things} did Benaiah the son of Jehoiada, and had the name among three mighty men.}
[23] \textcolor[rgb]{0.00,0.00,1.00}{He was more honourable than the thirty, but he attained not to the \emph{first} three. And David set him over his guard.}
[24] \textcolor[rgb]{0.00,0.00,1.00}{}
[25] \textcolor[rgb]{0.00,0.00,1.00}{}
[26] \textcolor[rgb]{0.00,0.00,1.00}{}
[27] \textcolor[rgb]{0.00,0.00,1.00}{}
[28] \textcolor[rgb]{0.00,0.00,1.00}{}
[29] \textcolor[rgb]{0.00,0.00,1.00}{}
[30] \textcolor[rgb]{0.00,0.00,1.00}{}
[31] \textcolor[rgb]{0.00,0.00,1.00}{}
[32] \textcolor[rgb]{0.00,0.00,1.00}{}





\newpage
