\section{Psalm 99 Comments}

\subsection{Numeric Nuggets}
\textbf{13: } The 13-letter word ``righteousness'' is used in the chapter.

\subsection{Psalm 99 Introduction}
This is another Millennial psalm. Ruckman points out the erroneous placement of the psalm by trusted modern clergy!\cite{Ruckman1992PsalmsV2}
\begin{compactenum}[I.]
	\item Mt Zion is interpreted as the church because it is God's ``favorite place.''
	\item The entire earth should be in awe of God sitting in heaven a sthe universal ``Monarch.''
	\item Spurgeon says, the ``rule of God'' can be felt by Christians today.\cite{spurgeon2016treasury}
	\item The message of the psalm is the ``mediatorial reign'' of Jesus Christ and of church leaders.
\end{compactenum}
If one held to an Amillennial or Postmillennial system of theology then one could not read the psalm as it is written  or interpret it correctly. The Lord is NOT now sitting on an earthly throne, but he will. And, as seen in verse 2, it will be in Zion.

\subsection{Psalm 99:1}
Apparently there is a seat where God is sitting and this seat is between things called ``cherubims''. We find ``cherubims'' 38 times in the AV, and ``cherubim's'' once. The first mention of cherubims is found in Genesis 3:24 where they are guarding and preventing fallen Adam from getting to the tree of life in Eden.\footnote{\textbf{Genesis 3:24} - So he drove out the man; and he placed at the east of the garden of Eden Cherubims, and a flaming sword which turned every way, to keep the way of the tree of life.}

This seat between the cherubims is where God is now seated.\footnote{\textbf{Revelation 4:6-9} - And before the throne there was a sea of glass like unto crystal: and in the midst of the throne, and round about the throne, were four beasts full of eyes before and behind. [7] And the first beast was like a lion, and the second beast like a calf, and the third beast had a face as a man, and the fourth beast was like a flying eagle. [8] And the four beasts had each of them six wings about him; and they were full of eyes within: and they rest not day and night, saying, Holy, holy, holy, Lord God Almighty, which was, and is, and is to come. [9] And when those beasts give glory and honour and thanks to him that sat on the throne, who liveth for ever and ever,} This seat is connected to the mercy seat in Numbers 7:89.\footnote{\textbf{Numbers 7:89} - And when Moses was gone into the tabernacle of the congregation to speak with him, then he heard the voice of one speaking unto him from off the mercy seat that was upon the ark of testimony, from between the two cherubims: and he spake unto him.} ``Between the churubims'' is where God sat in the tablernacle in the wilderness (Exodus 25:22)\footnote{\textbf{Exodus 25:22} - And there I will meet with thee, and I will commune with thee from above the mercy seat, from between the two cherubims which are upon the ark of the testimony, of all things which I will give thee in commandment unto the children of Israel.} and where Jesus is pictured at his return (Ezekiel 1:20-28).\footnote{\textbf{Ezekiel 1:20-28} - Whithersoever the spirit was to go, they went, thither was their spirit to go; and the wheels were lifted up over against them: for the spirit of the living creature was in the wheels. [21] When those went, these went; and when those stood, these stood; and when those were lifted up from the earth, the wheels were lifted up over against them: for the spirit of the living creature was in the wheels. [22] And the likeness of the firmament upon the heads of the living creature was as the colour of the terrible crystal, stretched forth over their heads above. [23] And under the firmament were their wings straight, the one toward the other: every one had two, which covered on this side, and every one had two, which covered on that side, their bodies. [24] And when they went, I heard the noise of their wings, like the noise of great waters, as the voice of the Almighty, the voice of speech, as the noise of an host: when they stood, they let down their wings. [25] And there was a voice from the firmament that was over their heads, when they stood, and had let down their wings.
[26] And above the firmament that was over their heads was the likeness of a throne, as the appearance of a sapphire stone: and upon the likeness of the throne was the likeness as the appearance of a man above upon it. [27] And I saw as the colour of amber, as the appearance of fire round about within it, from the appearance of his loins even upward, and from the appearance of his loins even downward, I saw as it were the appearance of fire, and it had brightness round about. [28] As the appearance of the bow that is in the cloud in the day of rain, so was the appearance of the brightness round about. This was the appearance of the likeness of the glory of the LORD. And when I saw it, I fell upon my face, and I heard a voice of one that spake.}

One of these cherubim, the fifth, is none other than Satan, who in one of his imitations of God, also now has a seat (Revelation 2:13).\footnote{\textbf{Revelation 2:13} - I know thy works, and where thou dwellest, even where Satan’s seat is: and thou holdest fast my name, and hast not denied my faith, even in those days wherein Antipas was my faithful martyr, who was slain among you, where Satan dwelleth.} From this seat, a religious throne, Satan now does his business in the religions of the world (but isn't there really only one?).

\subsection{Psalm 99:2}
The Lord is not only ``figuratively'' high above the people, but he is literally above the people, as the Second Advent will flatten all the hills and mountains of the earth except for Jerusalem, aka Zion. Now, Zion is at the top of the universe, the sides of the north.\footnote{\textbf{Psalm 48:2} - Beautiful for situation, the joy of the whole earth, is mount Zion, on the sides of the north, the city of the great King.}\footnote{\textbf{Isaiah 14:13} - For thou hast said in thine heart, I will ascend into heaven, I will exalt my throne above the stars of God: I will sit also upon the mount of the congregation, in the sides of the north:}

\subsection{Psalm 99:5}
The ``footstool'' is the earth (See Psalm 110:1, Isaiah 66:1, and Matthew 5:35).\footnote{\textbf{Psalm 110:1} - The LORD said unto my Lord, Sit thou at my right hand, until I make thine enemies thy footstool}\footnote{\textbf{Isaiah 66:1} - Thus saith the LORD, The heaven is my throne, and the earth is my footstool: where is the house that ye build unto me? and where is the place of my rest}\footnote{\textbf{Matthew 5:35} - Nor by the earth; for it is his footstool: neither by Jerusalem; for it is the city of the great King.}

\subsection{Psalm 99:8}
The word ``invent'' is used once in the AV, in Amos 6:5, and is connected to ``them that are at ease in Zion.''\footnote{\textbf{Amos 6:5} - That chant to the sound of the viol, and invent to themselves instruments of musick, like David;} The word ``inventions is used 5 times, here and in  Psalm 106:29,\footnote{\textbf{Psalm 106:29} - Thus they provoked him to anger with their inventions: and the plague brake in upon them.} Psalm 106:39,\footnote{\textbf{Psalm 106:39} - Thus were they defiled with their own works, and went a whoring with their own inventions.} Proverb 8:12,\footnote{\textbf{Proverb 8:12} - I wisdom dwell with prudence, and find out knowledge of witty inventions. } and Ecclesiastes 7:29.\footnote{\textbf{Ecclesiastes 7:29} - Lo, this only have I found, that God hath made man upright; but they have sought out many inventions.} One thinks of the ``engines of war'' built by cunning men in the days of Uzziah (2 Chronicles 26:15).\footnote{\textbf{2 Chronicles 26:15} - And he made in Jerusalem engines, invented by cunning men, to be on the towers and upon the bulwarks, to shoot arrows and great stones withal. And his name spread far abroad; for he was marvellously helped, till he was strong.} These can be likened to the same used by Nebuchadnezzar against Tyre in Ezekiel 26:9.\footnote{\textbf{Ezekiel 26:9} - And he shall set engines of war against thy walls, and with his axes he shall break down thy towers.} The examples provided in scripture put an interesting perspective on the function of engineers among mankind. Typically, new technologies have vast potential to improve the temporary lot of mankind (although they do nothing to solve the sin problem), but almost without fail the end up contributing to laziness, licenteousness, and the abuse of power. The verse in Amos gives a counterexample of David inventing musical instruments, as we see referenced in various psalms.
